Precise spiking motifs in neurobiological and neuromorphic data

### 2022-12-19 manuscript.tex
in sync

% a simpler annotation system:
\usepackage{soulutf8}
\usepackage{color}
\newcommand{\note}[1]{{\sethlcolor{yellow}\hl{#1}}}
\usepackage{trackchanges}

@@

% \note{redo a figure similar to the thorpe code}%\includegraphics{images/roc.jpg}

@@

There are different solutions to provide with a distance between two given spike trains. A known measure is the Victor-Purpura distance, which overcomes inconsistencies experienced with a \remove[JN]{simple} firing rate (Poisson model) of spike trains~\citep{victor_nature_1996}. \change[JN]{In a later study,van_rossum_novel_2001 have defined a distance that uses a time constant as a parameter}{Then a study tries to solve the problem by including a time constant as a parameter}~\citet{van_rossum_novel_2001}. \change[JN]{Depending on this parameter, the distance interpolates between a coincidence detector and a rate difference counter.}{This parameter will then be used to interpolate the distance between a coincidence detector and a rate difference counter.} Such distances were extended to non-Euclidean metrics and use morphological manipulations to compute spike train dissimilarity~\citep{kreuz_measuring_2007}. Mathematically, the stability of distance measures induced by level-crossing sampling can be evaluated~\citep{moser_stability_2014}, notably in light of the so-called Weyl's discrepancy measure~\citep{weyl_ueber_1916}, which may lead to the definition of a cross-correlation measure \change[JN]{which}{. An interesting conclusion since cross-correlation measure is} which is adapted to the event-based nature of spiking signals. These observations lead to the intuition that each distance may be as well  as the optimal solution of a generative model for these measures, possibly through non-linear relations~\citep{aronov_non-euclidean_2004}. % ~\citep{}

>>>>

% a simpler annotation system:
\usepackage{soulutf8}
\usepackage{color}
\newcommand{\mynote}[1]{{\sethlcolor{yellow}\hl{#1}}}
\usepackage{trackchanges}

@@

% \mynote{redo a figure similar to the thorpe code}%\includegraphics{images/roc.jpg}

@@

There are different solutions to provide with a distance between two given spike trains. A known measure is the Victor-Purpura distance, which overcomes inconsistencies experienced with a \remove[JN]{simple} firing rate (Poisson model) of spike trains~\citep{victor_nature_1996}. \change[JN]{In a later study, Van Rossum (2001) have defined a distance that uses a time constant as a parameter}{Then a study tries to solve the problem by including a time constant as a parameter}~\citet{van_rossum_novel_2001}. \change[JN]{Depending on this parameter, the distance interpolates between a coincidence detector and a rate difference counter.}{This parameter will then be used to interpolate the distance between a coincidence detector and a rate difference counter.} Such distances were extended to non-Euclidean metrics and use morphological manipulations to compute spike train dissimilarity~\citep{kreuz_measuring_2007}. Mathematically, the stability of distance measures induced by level-crossing sampling can be evaluated~\citep{moser_stability_2014}, notably in light of the so-called Weyl's discrepancy measure~\citep{weyl_ueber_1916}, which may lead to the definition of a cross-correlation measure \change[JN]{which}{. An interesting conclusion since cross-correlation measure is} which is adapted to the event-based nature of spiking signals. These observations lead to the intuition that each distance may be as well  as the optimal solution of a generative model for these measures, possibly through non-linear relations~\citep{aronov_non-euclidean_2004}. % ~\citep{}
